Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
address some g0 todos, minor edits elsewhere

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for grobner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non stacky) curves.
\end{enumerate}

\begin{rem}
\label{rem:delta-not-1}
Suppose $(\sx,\Delta,L)$ is a log spin curve. Note that $\deg \lfloor L \rfloor$ is even. because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K \rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even. In particular, we shall often use $\deg \Delta \neq 1$.
\end{rem}

@@

\begin{rem}
For our purposes, it is useful to call the saturation of the
effective monoid of a divisor $D$ as the saturation $s$ of the
divisor $D$ on $\sx$. In this case, the saturation $s$ of a divisor
$D$ on $\sx$ (i.e. $\sat(\Eff(D))$) is the smallest positive $s \in
\BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d \geq s$.
\end{rem}

@@

\todo{transition}
Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}
\todo{fill out}

@@

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma_2$ has saturation $s = 5$, \todo{Why is there a 's here instead of just s?} as noted in
Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
when $d \geq 21 + s = 25$ (i.e. $R'$ is generated up to degree 24). \todo{Aaron: Isn't $s + 21 = 26$? Shouldn't it be generated up to degree 25, potentially?}

@@

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
and $7 < d \leq 24$. \todo{Should this be 25?} Note that we can again use Max No ether's theorem
(taking saturation into account) to see that

@@

Furthermore, we can directly see that the relations are given
in degrees $10$ and $14$. In particular, we have relations
\begin{align*}
	a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} &= 0 & \text{ in degree $10$ and } \\
	b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 &= 0 & \text{ in degree $14.$ }
\end{align*}

@@

\ssec{Main Theorem for Genus Zero}
\label{ssec:g-0-main}
Now we can combine this.
\todo{write this section}

>>>>

\section{Background}
\label{sec:background}
Look at Spencer-Kodaira \cite{kodaira:complex-manifolds}.
Include the following:
\begin{enumerate}
	\item Notation for Coarse space
	\item Notation for Stacky points with associated stabilizer orders (I.e. as those points for which the divisor can have rational coefficients with denominator equal to the stabilizer order)
	\item Note that this result is independence of base field
	\item background on Gr\"{o}bner bases
	\item Notation $h^0 = \dim_k H^0$.
	\item Why we have these fractions $\frac{e_i - 1}{2e_i}$ and why $e_i$ must be odd.
	\item Include notation for $X$ as coarse space and $L_X$ the corresponding log half canonical divisor.
	\item Notation for Gr\"{o}bner bases and orderings (include grlex, grevlex, and block order, as defined in \cite[Definition 8.1.1]{vzb:stacky})
	\item Make sure to standardize the notation $\sx,\sx'$ for stacky curves, $L,L'$ for half canonical divisors, and $X,X'$ for (non-stacky) curves.
\end{enumerate}

\begin{rem}
\label{rem:delta-not-1}
Suppose $(\sx,\Delta,L)$ is a log spin curve. Note that $\deg \lfloor L \rfloor$ is even. because $2 \cdot \deg L = \deg \Delta + \deg \lfloor K \rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even. In particular, we shall often use $\deg \Delta \neq 1$.
\todo{This seems to actually be proving that $\deg \Delta$ is even}
\end{rem}

@@

\begin{rem}
For our purposes, it is useful to call the saturation of the
effective monoid of a divisor $D$ as the saturation $s$ of the
divisor $D$ on $\sx$. In this case, the saturation $s :=
\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
\geq s$.
\end{rem}

@@

\todo{transition}
Here we describe induction of raising degrees from Lemma ~\ref{lem:raise-stacky-order}

@@

\noindent
is surjective whenever $\deg (\lfloor (d - 21) K_{\sx'} \rfloor)
\geq 0$. Since $\sigma_2$ has saturation $s = 5$, as noted in
Subsection ~\ref{ssec:g_0_saturation}, then this map is surjective
when $d \geq 21 + s = 26$ (i.e. $R'$ is generated up to degree 25).

@@

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
and $7 < d \leq 25$. Note that we can again use Max No ether's theorem
(taking saturation into account) to see that

@@

Furthermore, we can directly see that the relations are given
in degrees $10$ and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{5, 1}^2 + a_2 x_{3, 1} x_{7, 1} + a_3 x_{3, 1} x_{7, 2} = 0 &\text{ in degree $10$} \\
	&b_1 x_{7, 1}^2 + b_2 x_{3, 1}^3 x_{5, 1} + b_3 x_{7, 1} x_{7, 2} + b_4 x_{7, 2}^2 = 0  &\text{ in degree $14$}
\end{align*}

@@

\ssec{Main Theorem for Genus Zero}
\label{ssec:g-0-main}
Now we can combine this.
